Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375

### 2015-03-10 papers/B1555_EdgeOn/B1555_letter.tex
Take off IR flux ratio in Table

%%table3
\begin{table}
\begin{center}
\caption{Flux Ratios of B1555+375 Components.\label{tbl-3}}
\begin{tabular}{lccccc}
\tableline\tableline
				&5 GHz & 15 GHz & Ks  &Model-predicted\\
\tableline
A/B			&$1.8$ & $1.8$ & $3.5$ &$1.7$  \\ 
A/C 		&$2.0$ 	&$2.4$ &$1.0$ &$2.2$  \\
A/D			&$13.0$ &$ 12.9$ & $5.4$ &$8.0$  \\
\tableline
\end{tabular}
%% Any table notes must follow the \end{tabular} command.
\tablecomments{Radio observation data quoted from Table 2 and Table 3 in \citet{Marlow}. Flux ratio between the merging double is much higher in infrared than in radio, which is believed to be caused by strong dust extinction from the edge-on disk.}
\end{center}
\end{table}

@@

\section{Discussion}
The abundance of substructure within galaxy-size halo has been an undetermined problem in structure formation studies. Discrepency between numerical simulation and observation within the Local Universe gives two possible interpretations: an alternative structure formation model or small sample from the Local Universe. Difficulties emerge while searching beyond the Local Group due to the low luminosity of satellites. This makes gravitational lensing a powerful tool for the detection of substructures. With the fact that surface brightness is sensitive to gravitational perturbation, flux ratio anomaly in strong lensing system becomes a sign of existence of subhalo and also reflects its total mass. Give directly measurement of mass function which can avoid making assumptions on how baryonic matter distributes with dark matter.

>>>>

%%table3
\begin{table}
\begin{center}
\caption{Flux Ratios of B1555+375 Components.\label{tbl-3}}
\begin{tabular}{lccccc}
\tableline\tableline
				&5 GHz & 15 GHz  &Model-predicted\\
\tableline
A/B			&$1.8$ & $1.8$ & $1.7$  \\ 
A/C 		&$2.0$ 	&$2.4$ &$2.2$  \\
A/D			&$13.0$ &$ 12.9$ & $8.0$  \\
\tableline
\end{tabular}
%% Any table notes must follow the \end{tabular} command.
\tablecomments{Comparision between radio data and model-predicted flux ratios. Radio observation data quoted from Table 2 and Table 3 in \citet{Marlow}.}
\end{center}
\end{table}

@@

\section{Discussion}
The abundance of substructure within galaxy-size halo has been an undetermined problem in structure formation studies. Discrepency between numerical simulation and observation within the local universe gives two possible interpretations: an alternative structure formation model or small sample from the Local Universe. Difficulties emerge while searching beyond the Local Group due to the low luminosity of satellites. This makes gravitational lensing a powerful tool for the detection of substructures. With the fact that surface brightness is sensitive to gravitational perturbation, flux ratio anomaly in strong lensing system becomes a sign of existence of subhalo and also reflects its total mass. Give directly measurement of mass function which can avoid making assumptions on how baryonic matter distributes with dark matter.
